%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[letterpaper]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PERSONAL INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\name{Christopher H. McKnight}{}
\address{Clarksville, TN}
\email{cmckni3@gmail.com}
\github{cmckni3}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
\begin{document}

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
{\today}
{}
{\thepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makecvheader[C]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
  \cventry
    {Lead Architect, Senior Consultant}
    {iOLAP}
    {Clarksville, TN (remote)}
    {August 2018 – Present}
    {\begin{cvitems}
      \item {Created APIs using node.js, MongoDB, Rabbitmq, and GraphQL.}
      \item {Created UIs in React and Angular.}
      \item {Built iOS and Android applications using NativeScript.}
      \item {Created a voice UI using Google Cloud Platform and Dialogflow.}
      \item {Created Dockerfiles for applications and setup Docker builds.}
      \item {Created CI/CD pipelines.}
      \item {Created an analysis application with the analytics team. Project used node.js, AWS Amazon ECS, Amazon Cognito, DynamoDB, Lambda, Rekognition, SNS, and SQS for backend services. Project used Angular for the UI.}
      \end{cvitems}}

  \cventry
    {Lead Front End Software Engineer}
    {Single Music}
    {Nashville, TN}
    {August 2017 – October 2019}
    {\begin{cvitems}
      \item {Implemented physical tagging feature along with bundles.}
      \item {Implemented BoostLinks marketing campaign feature.}
      \item {Implemented prettier for standardized JavaScript and TypeScript code style.}
      \item {Upgraded Angular applications from v2 to v4/v5/v6.}
      \item {Implemented audio player for Shopify themes.}
      \end{cvitems}}

  % \cventry
  %   {Front End Software Engineer III}
  %   {Franklin American Mortgage, A Division of Citizens Bank}
  %   {Franklin, TN}
  %   {August 2018 – August 2018}
  %   {\begin{cvitems}
  %     \item {Worked closely with API team to build out new APIs and make API changes.}
  %     \item {Created shared libraries and components for company Angular applications.}
  %     \item {Created scenario application in Angular for loan officers and clients to estimate fees and monthly payment.}
  %     \item {Created Angular application for construction loan status.}
  %     \item {Implemented prettier for standardized JavaScript and TypeScript code style.}
  %     \item {Upgraded Angular applications from v2 to v4/v5/v6.}
  %     \end{cvitems}}

  \cventry
    {Front End Software Engineer III}
    {Franklin American Mortgage Company}
    {Franklin, TN}
    {April 2018 – August 2018}
    {\begin{cvitems}
      \item {Worked closely with API team to build out new APIs and make API changes.}
      \item {Created shared libraries and components for company Angular applications.}
      \item {Created scenario application in Angular for loan officers and clients to estimate fees and monthly payment.}
      \item {Created Angular application for construction loan status.}
      \item {Implemented prettier for standardized JavaScript and TypeScript code style.}
      \item {Upgraded Angular applications from v2 to v4/v5/v6.}
      \end{cvitems}}

  \cventry
    {Developer II}
    {Franklin American Mortgage Company}
    {Franklin, TN}
    {October 2016 – April 2018}
    {\begin{cvitems}
      \item {Created new API endpoints for PHP applications.}
      \item {Developed image editing application in Angular (v2+).}
      \item {Created Docker images for dashboards.}
      \item {Deployed dashboards to Kubernetes cluster.}
      \item {Implemented SAML SSO in Java application for Wordpress Single Sign On.}
      \item {Created scenario application in Angular for loan officers and clients to estimate fees and monthly payment.}
      \item {Created Angular application for construction loan status.}
      \end{cvitems}}

  \cventry
    {Senior Software Developer}
    {Immense Networks}
    {Baton Rouge, LA}
    {October 2011 - September 2016}
    {\begin{cvitems}
      \item {Managed PHP applications using WHM/cPanel.}
      \item {Wrote custom PHP applications using symfony 1.4, propel, jQuery, and MySQL.}
      \item {Developed and deployed Ruby on Rails applications using nginx and Passenger Enterprise.}
      \item {Developed, maintained, and deployed node.js web applications using nginx.}
      \item {Created user interfaces in web applications using HTML, JavasScript, Bootstrap, and knockout.js.}
      \item {Created a conference registration application on node.js using Coffeescript, MongoDB, and PayPal. Created the user interface using HTML, JavaScript, Bootstrap, and knockout.js.}
      \item {Created a Ruby on Rails application for employees and managers to bill equipment time. The application computed employee salary, wages, and overtime. Finally, the application helped find discrepancies between employee and equipment time. The Ruby on Rails backend used MySQL for application data storage and accessed employee data through SQL Server. The application was later migrated to use Vista by Viewpoint (SQL Server 2014) instead of NexGen (SQL Server 2005).}
      \item {Utilized CocoaPods for managing 3rd Party iOS dependencies.}
      \item {Redesigned the Contact Mover iOS application to copy contacts to be user friendly and reach a larger customer base.}
      \item {Created the La. Contractor iOS application to search for licensed contractors in the state of Louisiana. Designed the contractor search JSON API as well.}
      \item {Developed an iOS application to track tools using the Linea Pro barcode scanner. The application submits GPS coordinates to a node.js API when unloaded. Utilized RestKit and AFNetworking for API requests. Later switched to using Mantle and AFNetworking for object mapping and caching. Deployed the application using MobileIron MDM.}
      \item {Designed, developed, and deployed custom enterprise iOS applications.}
      \item {Created the PHP implementation of Macaroons for decentralized authorization.}
      \item {Converted a PHP symfony 1.4 application to use Macaroons for authorization.}
      \item {Designed and implemented JSON APIs for multiple Ruby on Rails, PHP, and node.js applications.}
      \end{cvitems}}

  % \cventry
  %   {Master Residential Student Technician}
  %   {Louisiana State University Residential Life}
  %   {Baton Rouge, LA}
  %   {February 2009 - October 2011}
  %   {\begin{cvitems}
  %     \item {Ensured computer labs are fully operational including printers.}
  %     \item {Assisted in training new technicians.}
  %     \item {Created a PHP application to manage Residential Life television images.}
  %     \item {Created a PHP time tracking application.}
  %     \item {Created Norton Ghost images for Windows XP, Windows 7, and Macintosh workstations.}
  %     \item {Completed equipment transfers and inventory.}
  %     \end{cvitems}}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Skills}
\begin{cvskills}
  \cvskill
    {Programming Languages}
    {JavaScript, Objective-C, Ruby, TypeScript, PHP}

  \cvskill
    {Cloud Platform Technologies}
    {AWS API Gateway, AWS Cognito, AWS CDK, AWS CloudFormation, AWS DynamoDB, AWS ECS, AWS Lambda}

  \cvskill
    {Frameworks}
    {Angular, express.js, iOS, koa, Ruby on Rails, symfony}

  \cvskill
    {Libraries/Technologies}
    {Auth0, AJAX, GraphQL, jQuery, JSON, knockout.js, Macaroons, ngrx, Okta, Promise, RxJS, window.fetch}

  \cvskill
    {Databases}
    {MongoDB, MySQL, SQL Server}

  \cvskill
    {Tools}
    {Git, babel, webpack}

  \cvskill
    {DevOps}
    {apache, Docker, Kubernetes, Linux, nginx, Passenger, Passenger Enterprise}
\end{cvskills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
  \cventry
    {Bachelor of Science, Computer Science}
    {Louisiana State University}
    {Baton Rouge, LA}
    {December 2011}
    {Mathematics Minor \& Second Discipline}
\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Certifications}
\begin{cventries}
  \cventry
    {
      \href{https://www.youracclaim.com/badges/03730776-b911-43ac-8d3a-99f3f4513162/public_url}{AWS Certified Solutions Architect - Professional (SAP)}
    }
    {March 2020 - March 2023}
    {Credential ID: 8XL9W4KK3JREQF9K}
    {}
    {}

  \cventry
    {
      \href{https://www.youracclaim.com/badges/d0c32f27-054b-432c-9fd1-8d3e912a9396/public_url}{AWS Certified DevOps Engineer - Professional (DOP)}
    }
    {February 2020 - February 2023}
    {Credential ID: 3GNHJVH1PJ4QQL9N}
    {}
    {}

  \cventry
    {
      \href{https://www.youracclaim.com/badges/b908a72e-7d86-41f1-9715-d8a035f07b70/public_url}{AWS Certified Alexa Skill Builder - Specialty (AXS)}
    }
    {February 2020 - February 2023}
    {Credential ID: BYPQ3FXCHB141T35}
    {}
    {}

  \cventry
    {
      \href{https://www.youracclaim.com/badges/8e12bd33-2fa9-4ea9-bc06-b6a34cba1ca1/public_url}{AWS Certified Big Data - Specialty (BDS)}
    }
    {June 2020 - June 2023}
    {Credential ID: ZQ5NDBM1FJB41EG9}
    {}
    {}

  \cventry
    {
      \href{https://www.youracclaim.com/badges/70174d02-8350-4f34-9d9d-26b3e8f3341d/public_url}{AWS Certified Data Analytics – Specialty (DAS)}
    }
    {August 2020 - August 2023}
    {Credential ID: MGHXZ4NCP1VQQZKD}
    {}
    {}

  \cventry
    {
      \href{https://www.youracclaim.com/badges/33206a04-66c4-41df-877b-db34ffcb93a8/public_url}{AWS Certified Security - Specialty (SCS)}
    }
    {December 2019 - December 2022}
    {Credential ID: 4JJXEQR2NJ41Q6SL}
    {}
    {}

  \cventry
    {
      \href{https://www.youracclaim.com/badges/b0cd52af-b58f-44ff-aa19-b189ce841629/public_url}{AWS Certified Solutions Architect - Associate (SAA)}
    }
    {September 2019 - March 2023}
    {Credential ID: CJE2GNRKG2V119SK}
    {}
    {}

  \cventry
    {
      \href{https://www.youracclaim.com/badges/afffcfaa-b3d0-4d2b-8d3e-71c281150763/public_url}{AWS Certified Developer - Associate (DVA)}
    }
    {October 2019 - February 2023}
    {Credential ID: WL82LHC23BV1Q6G4}
    {}
    {}

  \cventry
    {
      \href{https://www.youracclaim.com/badges/b3409740-de23-4249-939b-81abe72624cb/public_url}{AWS Certified SysOps Administrator - Associate (SOA)}
    }
    {January 2020 - February 2023}
    {Credential ID: 5SMFHPT1HNB1QZK2}
    {}
    {}

  \cventry
    {
      \href{https://www.youracclaim.com/badges/d8fc811b-6cda-46d0-a1b1-1aee5e390dd1/public_url}{AWS Certified Cloud Practitioner (CLF)}
    }
    {January 2020 - March 2023}
    {Credential ID: YVCEMRXCF24E1Q98}
    {}
    {}

\end{cventries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Presentations
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Presentations}
\begin{cventries}
  \cventry
    {Fundamentals of Git}
    {Refresh Baton Rouge Meetup}
    {Baton Rouge, LA}
    {March 26, 2015}
    {
      \begin{cvitems}
        \item {Explained how to start a project using Git.}
        \item {Discussed committing, pushing, and merging in depth with a demo.}
      \end{cvitems}
    }

  \cventry
    {Angular Deep Dive}
    {Franklin American Mortgage Company \& All Things Angular}
    {Franklin, TN}
    {April 21, 2017 \& April 25, 2017}
    {
      \begin{cvitems}
        \item {Explained directives, components, services, and templates.}
        \item {Described container and presentation components.}
        \item {Demonstrated best practices including one way data flow.}
        \item {Concluded with an Angular application walkthrough.}
      \end{cvitems}
    }

  \cventry
    {AngularJS to Angular Migration}
    {All Things Angular}
    {Franklin, TN}
    {August 29, 2017}
    {
      \begin{cvitems}
        \item {Showed a few methods to migrate an application from AngularJS to Angular.}
      \end{cvitems}
    }

  \cventry
    {Angular Authentication}
    {All Things Angular}
    {Franklin, TN}
    {May 29, 2018}
    {
      \begin{cvitems}
        \item {Discussed Authentication using using OAuth2.}
        \item {Demonstrated Firebase Authentication.}
      \end{cvitems}
    }

  \cventry
    {NativeScript}
    {All Things Angular}
    {Franklin, TN}
    {October 23, 2018}
    {
      \begin{cvitems}
        \item {Showed an overview of NativeScript.}
        \item {Demonstrated NativeScript app building using the cli and playground.}
        \item {Discussed shortcomings of NativeScript.}
        \item {Answered questions about NativeScript vs other technologies vs native.}
      \end{cvitems}
    }
\end{cventries}

\end{document}
